Point-process based representation learning for Electronic Health Records

### 2023-02-08 Manuscript_v1.tex
update

>>>>

Consider an event sequence data  $\mathcal{D}=\{\mathcal{S}_{i}\}_{i=1}^N$ where each sample is represented as an event sequence  $\mathcal{S}_{i}=\{(t_i,e_i)\}_{j=1}^L$, where $L$ is number of event, $t_j$ is event's timestamp, and $e_j \in \mathbb{R}^M $ is the binary represntation of event marks (multi-class or multi-label). The history of events is denoted as $\mathcal{H}_t=\{(t_j,e_j):t_j<t \} $

In the multi-class setting where each mark can be exactly one of M marks, the point process is characterized by $M$ conidtional intensity functions (CIFs):

\begin{equation}\label{eq:11}
   \lambda_m^{*}(t)=\lim \frac{P(  \text{event of type m in } [t,t+\Delta t) |   \mathcal{H}_t  )}{\Delta t} 
\end{equation}

The default negative log-likelihood (NLL) of a point process for a single event sequnce $\mathcal{S}_{i}$ is defined as:

\begin{multline}\label{eq:11}
    -\log p(\mathcal{S}_{i})  =  - \sum_{j = 1}^{L}\sum_{m = 1}^{M} 1(e_j=m)   \log \lambda_m^{*}(t_j) \\   
    + \sum_{m = 1}^{M} \left(   \int_{0}^{T}  \lambda_m^{*}(s) \,ds  \right)
\end{multline}

If we assume that marks and events are independent,

\begin{multline}\label{eq:11}
    -\log p(\mathcal{S}_{i})  = \\
      - \sum_{j = 1}^{L}\sum_{m = 1}^{M} 1(e_j=m)   \log p^{*}(e_j=m) \lambda^{*}(t_j) \\   
    + \sum_{m = 1}^{M} p^{*}(e_j=m) \left(   \int_{0}^{T}  \lambda_m^{*}(s) \,ds  \right)
\end{multline}

[ntpp] has proposed to extend for mult

marked cased

relation to autoencoder
